Quotient Normalized Maximum Likelihood Criterion for Learning Bayesian Network Structures

### 2017-10-11 main.tex
consistency proof reformulated a bit
A bit more on approximations
finetuning
definition environment added
use aistats2018 package

\documentclass[letterpaper]{article}
\usepackage{proceed2e}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsthm,epsfig,booktabs}

\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}

% Set the typeface to Times Roman
\usepackage{times}

\title{Quotient Normalized Maximum Likelihood Criterion for Learning Bayesian Network Structures}

@@

\maketitle

@@

\subsubsection*{Acknowledgements}

Use unnumbered third level headings for the acknowledgements title.
All acknowledgements go at the end of the paper.

>>>>

%\documentclass[letterpaper]{article}
%\usepackage{proceed2e}
%\usepackage[margin=1in]{geometry}

\documentclass[twoside]{article}
\usepackage{aistats2018}
\usepackage{amsmath,amsthm,epsfig,booktabs,multirow}
\usepackage{hyperref}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newcommand{\Le}{\left(}
\newcommand{\Ri}{\right)}

% Set the typeface to Times Roman
%\usepackage{times}

%\title{Quotient Normalized Maximum Likelihood Criterion for Learning Bayesian Network Structures}

@@

\twocolumn[

\aistatstitle{Quotient Normalized Maximum Likelihood Criterion for Learning Bayesian Network Structures}

\aistatsauthor{ Author 1 \And Author 2 \And  Author 3 }

\aistatsaddress{ Institution 1 \And  Institution 2 \And Institution 3 } ]

%\maketitle

@@

%%\subsubsection*{Acknowledgements}

%%Use unnumbered third level headings for the acknowledgements title.
%%All acknowledgements go at the end of the paper.
